Is malaria control profitable? Return on investment of privately-managed residential

### 2018-05-11 inst/rmd/paper.Rmd
last save before big clear

---
title: Is malaria control profitable? Return on investment of privately-managed residential fumigations at a large sugarcane processing facility in Southern Mozambique
date: ''
output: 
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: preamble.sty
fig_width: 4
fig_height: 2.6
bibliography: bibliography.bib
csl: journal-of-health-economics.csl
---

>>>>

---
title: Is malaria control profitable? Return on investment of privately-managed residential
  fumigations at a large sugarcane processing facility in Southern Mozambique
csl: apa_modified.csl
date: ''
output:
  word_document: default
  pdf_document:
    includes:
      in_header: preamble.sty
    keep_tex: yes
    latex_engine: xelatex
fig_width: 4
fig_height: 2.6
bibliography: bibliography.bib
---
